### 2020-12-13 paper/sections/introduction.tex
modify bib and simplify content
major introduction

\label{Section: introduction}
%With the increasing demand for continuous video analytics in public safety and transportation, more and more cameras are being deployed to various locations. The video analytics are based on classical computer vision techniques as well as deep convolutional neural networks. In recent years, we have also witnessed the emergence of a large number of excellent models for target detection \cite{trade-offs}, such as FasterRCNN \cite{ren2015faster_rcnn}, RFCN \cite{dai2016r_fcn}, Multibox \cite{szegedy2014multibox}, SSD \cite{liu2016ssd} and YOLO \cite{redmon2016yolo}.

%For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics.

A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is video analytics \emph{configuration}, and the configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}.

Different configurations directly affect accuracy and resource consumption. The best configuration is the one with the lowest resource demand whose accuracy is over the desired threshold, whcih can optimize the \emph{trade-off} between accuracy and energy consumption. The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}. As shown in figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g. only profiles the processing pipeline \emph{once} to choose high frame rate and resolution) can be very precise, but it can also be a huge drain on resource consumption. Similarly, specifying a fixed static cheap (e.g., low resolution and small model) configuration will significantly reduce accuracy. The brief framework of our solution %To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework
is shown in Figure~\ref{fig: framework}(b). In this, we tackle the following design challenges.

\begin{figure*}[!t]
	%\begin{tabular}{cc}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.8\linewidth]{figures/static_framework.pdf}}
		\begin{center}
			{(a) Static configuration solution: fixed configuration for video analytics services}
		\end{center}
		%        \vspace{0.3cm}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.8\linewidth]{figures/auto_framework.pdf}}
		\vspace{0.2cm}
		\begin{center}
			{(b) AdaConfigure solution: reinforcement learning-based adaptive configuration framework}
		\end{center}
	\end{minipage}
	%\end{tabular}
	%\vspace{0.1cm}
	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the object detection model feedback}
	%	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
	\label{fig: framework}
\end{figure*}

\begin{itemize}	
	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to solve by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space. For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly, but each condition may vary by hour, minute, even second. Spatially, the characteristics of video content are different in different locations. For instance, cameras in downtown areas show more cars than the other cameras deployed in the suburbs. It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video characteristics.
	%As a dynamic video analytics configuration %solution
	%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

	\item \emph{Adaptive configuration would cause a huge extra overhead.} %The number of possible configurations grows exponentially, 
There are thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}. So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations. To significantly reduce the resource cost for adaptive configuration profiling requires one solution that automaticly choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{wang2020jcab,jiang2018chameleon}, since their approach pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.

@@

\begin{itemize}	
	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to intrusive dynamics of video contexts. Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context. For the state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation. For the reward, we carefully consider both inference accuracy and computation resources to assess each configuration's impact. Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents. Our solution can adaptively update configuration strategy over time, and it adaptive to different location-camera inferences and different accuracy-demand services.
	%	 We design an interactive training environment that can be applied to different video analytics applications.
	%	\item We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analytics after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.

	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost. In the evaluation, AdaConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources. Our solution proves to be more efficient than static solutions and only creates an overhead of 0.2-2\% to the overall video analytics services.
\end{itemize}

>>>>

\label{Section: introduction}
%With the increasing demand for continuous video analytics in public safety and transportation, more and more cameras are being deployed to various locations. The video analytics are based on classical computer vision techniques as well as deep convolutional neural networks. In recent years, we have also witnessed the emergence of a large number of excellent models for target detection \cite{trade-offs}, such as FasterRCNN \cite{ren2015faster_rcnn}, RFCN \cite{dai2016r_fcn}, Multibox \cite{szegedy2014multibox}, SSD \cite{liu2016ssd} and YOLO \cite{redmon2016yolo}.
%For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics. 
A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution,  detector model selection and so on. A combination of the knob values is video analytics \emph{configuration}, and the configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}.
%(e.g., SSD \cite{liu2016ssd}+{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN \cite{ren2015faster_rcnn}+\{ResNet \cite{he2016resnet},InceptionResNet \cite{szegedy2016inception}\}).

Different configurations directly affect accuracy and resource consumption. The best configuration is the one with the lowest resource demand whose accuracy is over the desired threshold, whcih can optimize the \emph{trade-off} between accuracy and energy consumption. The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}. As shown in Figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g. only profiles the processing pipeline \emph{once} to choose high frame rate and resolution) can be very precise, but it can also be a huge drain on resource consumption. Similarly, specifying a fixed static cheap configuration (e.g., low resolution and small model) will significantly reduce accuracy. The framework of our solution %To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework
is shown in Figure~\ref{fig: framework}(b), and we tackle the following design challenges.

\begin{figure*}[!t]
	%\begin{tabular}{cc}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.9\linewidth]{figures/static_framework.pdf}}
		\begin{center}
			{(a) Static configuration solution: fixed configuration for video analytics services}
		\end{center}
		%        \vspace{0.3cm}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.9\linewidth]{figures/auto_framework.pdf}}
		\vspace{0.2cm}
		\begin{center}
			{(b) AdaConfigure solution: reinforcement learning-based adaptive configuration framework}
		\end{center}
	\end{minipage}
	%\end{tabular}
	%\vspace{0.1cm}
	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the object detection model feedback}
	%	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
	\label{fig: framework}
\end{figure*}

\begin{itemize}	
	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to be solved by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space. For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly. Spatially, the characteristics of video content are different in different locations. For instance, cameras in downtown areas show more cars than the other cameras deployed in the suburbs. It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video characteristics.
%	but each condition may vary by hour, minute, even second.
	%As a dynamic video analytics configuration %solution
	%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

	\item \emph{Adaptive configuration would cause a huge extra overhead.} %The number of possible configurations grows exponentially, 
	There are thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}. So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations. To significantly reduce the resource cost for adaptive configuration profiling requires one solution that automaticly choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{wang2020jcab,jiang2018chameleon}, since their approaches pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.

@@

\begin{itemize}	
	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to the characteristics of the video stream. For the agent's state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation.

	\item To reduce profiling cost, we leverage a video segmentation strategy and the extremely short choosing action time of agent. In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk, and then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds).
%to capture the characteristics of the video stream with much-reduced computation cost: profiling a segment uses only 0.2-2\% computation resource as compared to a full video.
%	Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.

	\item For the agent's reward, we carefully consider both inference accuracy and computation resources to assess each configuration's impact. Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents. Our solution can adaptively update configuration strategy over time, and it adaptive to different location-camera inferences and different accuracy-demand services.

% 	First, we design a reinforcement learning-based framework in which an agent adaptively chooses the configuration according to the spatial and temporal features of the current video stream.
	%	 We design an interactive training environment that can be applied to different video analytics applications.
	%	\item We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analytics after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.

%	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost. In the evaluation, AdaConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources. Our solution proves to be more efficient than static solutions and only creates an overhead of 0.2-2\% to the overall video analytics services.

%	\item Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 60-90% of the computation resource. 
\end{itemize}

### 2020-12-13 paper/sections/relatedwork.tex
major introduction

%\subsection{Configuration optimization} 
\subsection{Static configuration optimization}
Several previous papers have considered optimizing video analytics services by either adjusting the configuration knobs or training specialized NN models. VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations. VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations. MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints. Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingests and video query. By tuning the share of computing resources of both phases, Focus achieves an effective and flexible tradeoff of video analytics's latency and accuracy. These algorithms all profile and optimize video analytics only once at the beginning of the video. In their works, video is divided into pictures at a constant frame rate, and the work of video analysis is regarded as a fixed task either. In other words, they do not handle changes in video stream context. But the optimal configurations do change over time because of the complex and changeable video stream contexts.

>>>>

%\subsection{Configuration optimization} 
\subsection{Static Configuration Optimization}
Several previous papers have considered optimizing video analytics services by either adjusting the configuration knobs or training specialized NN models. VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations. VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations. 
%MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints. 
Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingests and video query. By tuning the share of computing resources of both phases, Focus achieves an effective and flexible tradeoff of video analytics's latency and accuracy. These algorithms all profile and optimize video analytics only once at the beginning of the video. In their works, video is divided into pictures at a constant frame rate, and the work of video analysis is regarded as a fixed task either. In other words, they do not handle changes in video stream context. But the optimal configurations do change over time because of the complex and changeable video stream contexts.
